FinalManuscript_DISCS_UG

### 2018-06-25 parts/01_introduction_01contextofstudy.tex

Digital data privacy and security is a growing concern in various fields, such as  cloud computing \cite{potey_homomorphic_2016}, health information systems \cite{kester_cryptographic_2015}, and video surveillance \cite{upmanyu_efficient_2009}. To meet these needs, various cryptosystems have been developed. A cryptosystem is a system which operates on plaintexts, ciphertexts and keys. a cryptosystem also has an encryption algorithm, which maps a plaintext to a ciphertext, and a decryption algorithm, which maps a ciphertext to a plaintext, given an appropiate key \cite[p.119]{tilborg_encyclopedia_2005}. The encryption and decryption algorithms are chosen such that the plaintext cannot easily be recovered from the ciphertext without knowledge of the key. This allows data to be securely transmitted over an insecure channel:  and thus much research has been done on the development and application of various cryptosystems.

>>>>

Digital data privacy and security is a growing concern in various fields, such as  cloud computing \cite{potey_homomorphic_2016}, health information systems \cite{kester_cryptographic_2015}, and video surveillance \cite{upmanyu_efficient_2009}. To meet these needs, various cryptosystems have been developed. A cryptosystem is a system which operates on plaintexts, ciphertexts and keys. a cryptosystem also has an encryption algorithm, which maps a plaintext to a ciphertext, and a decryption algorithm, which maps a ciphertext to a plaintext, given an appropiate key \cite{bauer_cryptosystem_2005}. The encryption and decryption algorithms are chosen such that the plaintext cannot easily be recovered from the ciphertext without knowledge of the key. This allows data to be securely transmitted over an insecure channel:  and thus much research has been done on the development and application of various cryptosystems.

### 2018-06-25 parts/01_introduction_02researchquestions.tex

To answer this question, we will consider the following sub-questions in our research:
\begin{enumerate}
    \item Which homomorphic image encryption algorithms are the most efficient in terms of time when applying image manipulation operations?
    \item Which homomorphic image encryption algorithms are the most secure under statistical attacks?
    \item How can a library for OpenCV be implemented for further use and study of image manipulation operations within a homomorphic cryptosystem?
\end{enumerate}

>>>>

To answer this question, we will consider the following sub-questions in our research:
\begin{enumerate}
	\item Which homomorphic image encryption algorithms are the most applicable for image processing operations?
	\item Which homomorphic image encryption algorithms are the most efficient in terms of time when applying image manipulation operations?
	\item Which homomorphic image encryption algorithms are the most secure under differential and entropy attacks?
\end{enumerate}

### 2018-06-25 parts/01_introduction_04significanceofstudy.tex

The results of the study will provide

>>>>

This study aims to directly address one of the current problems in the research of homomorphic cryptosystems: the practicality of homomorphic encryption \cite{sen_homomorphic_2013}. The literature shows existing homomorphic cryptosystems and how they support primitive operations (usually addition and multiplicaiton) on encrypted data, however, for homomorphic cryptosystems to be usable for practical image processing applications, support for more complicated operations such as image convolution must be demonstrated as well. While implementations of homomorphic encryption algorithms exist \cite{ziad_cryptoimg:_2016, garay_algorithms_2014}, our study targets algorithms for which statistical tests were not performed for image processing operations.

By developing a library allowing for the use and comparison of various homomorphic encryption algorithms, we wish to contribute to existing models for the secure transmission and modification of image data. Examples include applications in cloud storage \cite{potey_homomorphic_2016} and video surveillance \cite{upmanyu_efficient_2009}. This allows service providers to perform image manipulation for clients without compromising data privacy.
